\begin{abstract}
Traffic classification occupies a significant role in cybersecurity and network management. 
The widespread of encryption transmission protocols such as SSL/TLS has led to the dominance of deep learning based approaches.
In cybersecurity, strong adversaries often complicate their strategies by constantly developing emerging attacks. 
Meanwhile, security practitioners desire to grasp the reasons for inference results. 
However, existing deep learning approaches lack efficient adaptation for incremental traffic types and often have less interpretability. 
In this paper, we propose \sys, an Incremental and Interpretable Recurrent Neural Network for encrypted traffic classification.  
The \sys proposes a novel propagation process to extract the sequence fingerprints from sessions with local robustness. 
Meanwhile, this proposal provides interpretability including time-series feature attribution and inter-class similarity portrait. 
Moreover, we design \sys in an incremental manner to adapt to emerging traffic types. 
The \sys only needs to train an additional set of parameters for the newly added traffic type rather than retraining the whole model with the entire dataset.  
Extensive experimental results show that our \sys can achieve remarkable performance in traffic classification, incremental learning, and model interpretability. 
Compared with other local interpretability methods, our \sys exhibits excellent stability, robustness, and effectiveness in the interpretation of network traffic data.
\end{abstract}