\author{Zhuoxue~Song,~%~\IEEEmembership{Member,~IEEE,
	     Ziming~Zhao,~%~\IEEEmembership{Fellow,~OSA,}
            Fan~Zhang\textsuperscript{\Envelope},~\IEEEmembership{Member,~IEEE},~
	     Gang~Xiong,~\\%~\IEEEmembership{Member,~IEEE},~\\%\IEEEmembership{Member,~IEEE},~\\
            Guang~Cheng,~\IEEEmembership{Member,~IEEE},~%\IEEEmembership{Member,~IEEE},~
            Xinjie~Zhao,~
            and~Shize~Guo\textcolor{white}{\textsuperscript{\Envelope}}% <-this % stops a space

\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Zhuoxue Song, Ziming Zhao, Xinjie Zhao, and Shize Guo are with the College of Computer Science and Technology, Zhejiang University, Hangzhou 310027, China. E-mail: \{songzhuoxue, zhaoziming\}@zju.edu.cn.%\protect\\
\IEEEcompsocthanksitem Fan Zhang is with the College of Computer Science and Technology, Zhejiang University, Hangzhou 310027, with ZJU-Hangzhou Global Scientific and Technological Innovation Center, Hangzhou 311200, with the Key Laboratory of Blockchain and Cyberspace Governance of Zhejiang Province, with Jiaxing Research Institute, Zhejiang University, Jiaxing 314000, and also with Zhengzhou Xinda Institute of Advanced Technology, Zhengzhou 450001, China. E-mail: fanzhang@zju.edu.cn.%\protect\\
\IEEEcompsocthanksitem Gang Xiong is with the Institute of Information Engineering, Chinese Academy of Sciences, Beijing 100190, China. E-mail: xionggang@iie.ac.cn.%\protect\\
\IEEEcompsocthanksitem Guang Cheng is with the School of Cyber Science and Engineering, Southeast University, Nanjing 211189, China. E-mail: chengguang@seu.edu.cn.%\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
%\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.
}% <-this % stops an unwanted space

\thanks{
Manuscript received 17 Feb. 2022; revised 10 Nov. 2022. (Corresponding author: Fan Zhang.)}
}